### 2013-07-24 4/polsar_ivm.tex
updated for Ian to change

In this section the multiplicative nature of POLSAR data is illustrated.
Log-transformation is shown able to convert this into a more familiar additive model.
Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
  is proved to be the case for the original POLSAR data.
In log-transformed domain, the case for a homoskedastic model,
  whose variance is fixed and be independent of the underlying mean,
  is demonstrated.
To keep the section flowing, the mathematical derivation is only presented here in major sketches.
For more detailed derivation, please refer to Appendix \ref{chap:appendix_a}.

@@

Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
However, that would also require some iterative computations.
%***IVM: Hai, what does this mean "var [ln|Cv |]"? Is it an equation? You show it in text mode!!!
A more practical approach is to use a look-up graph approach
  where for each value of $var [ln|Cv|]$, a corresponding pre-computed value for L can be found by referencing the variance value on the graph.
An approximation can also be used  to find the L value based on a back-of-the-envelope calculation using the following equation  
  \begin{equation}
    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
    \label{eqn:enl_estimation_formula}
    \caption{eqn:ENL Estimation Formula for POLSAR data}
  \end{equation}
Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
  shows the shapes of the function defined in Eqn. \ref{eqn:var_log_det_is_homoskedastic} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$,
  together with the   approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
It can be seen that they are practically the same, hence the validity of Eqn \ref{eqn:enl_estimation_formula}.
In the next section, the estimated ENL will hence be used to demonstrate the accuracy of the proposed model.

@@

@@

In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
The representative power of the observable is explained in a few different ways.
Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
In fact, this chapter also proposes several new discrimination measures for POLSAR,
  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
%Such applications are briefly explored in the next chapter. 
The next chapter will briefly explore such applications as well as presents further validation of the proposed models.

>>>>

In this section the multiplicative nature of POLSAR data is illustrated.
Log-transformation is shown able to convert this into a more familiar additive model.
Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
  is proved to be the case for the original POLSAR data.
In log-transformed domain, the case for a homoskedastic model,
  whose variance is fixed and be independent of the underlying mean,
  is demonstrated.
To keep the section flowing, the mathematical derivation is only presented here in major sketches.
For more detailed derivation, please refer to Appendix \ref{sec:appendix_a}.

@@

Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
However, that would also require some iterative computations.
%***IVM: Hai, what does this mean "var [ln|Cv |]"? Is it an equation? You show it in text mode!!!
A more practical approach is to use a look-up graph approach
  where for each value of var [ln|Cv |], a corresponding pre-computed value for L can be found by referencing the variance value on the graph.
An approximation can also be used  to find the L value based on a back-of-the-envelope calculation using the following equation  
  \begin{equation}
    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
    \label{eqn:enl_estimation_formula}
    \caption{eqn:ENL Estimation Formula for POLSAR data}
  \end{equation}
Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
  shows the shapes of the function defined in Eqn. \ref{eqn:var_log_det_is_homoskedastic} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$,
  together with the   approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
It can be seen that they are practically the same, hence the validity of Eqn \ref{eqn:enl_estimation_formula}.
In the next section, the estimated ENL will hence be used to demonstrate the accuracy of the proposed model.

@@

In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
The representative power of the observable is explained in a few different ways.
Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
In fact, this chapter also proposes several new discrimination measures for POLSAR,
  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
Such applications are briefly explored in the next chapter.

@@
